Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-01-15 ms5n17-tlp-mn-180216-001.tex
few corrections

\documentclass[preprint,12pt]{article}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,authblk,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\affil[1]{School of Chemistry, University of Southampton, Southampton SO17 1BJ, United Kingdom}
\date{\today}
\setcounter{Maxaffil}{0}
\renewcommand\Affilfont{\itshape\footnotesize}
\clearpage

@@

Microfluidic NMR (Nuclear Magnetic Resonance) can probe chemical or bio-chemical reactions, including the metabolism of cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment. We present a dual-channel modular probe assembly for  high efficiency microfluidic-NMR. The samples are contained in exchangeable, flow compatible planar microfluidic devices. The detector including the tuning and matching circuitry of the probe is modular and allows the use of different detectors optimised for different experimental conditions on the same probe base. The complete probe can be built from easily available parts. The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit board) materials. The probe has a limit of detection of 1.18 nmol s$^{-1/2}$, resolution of 3.35 Hz and, excellent B$_{1}$ homogeneity. The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel ($^{13}$C or $^{15}$N) frequencies. We have successfully acquired $^1$H-$^{13}$C and $^1$H-$^{15}$N heteronuclear correlation spectrum (HSQC). Particularly, $^1$H-$^{15}$N HSQC spectrum of 1 mM $^{15}$N labeled ubiquitin from 2.5 $\mu$l of sample volume.

@@

\clearpage

@@

metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, molecular 
structure determination~\cite{wuthrich1990protein}, reaction 

@@

NMR spectroscopy can provide a useful complementary readout capability 
for microfluidic devices. For example, the metabolic activity of cell cultures 
can be followed non-invasively by NMR throughout the course of the experiment, 
while effects on cell differentiation can still be analysed by a (destructive) 
transcriptomic analysis at the end. Unfortunately, the sensitivity 
of NMR is much lower than that of optical techniques. 
The small volumes involved in microfluidic systems
 (typically in the range of 1~$\mu$l) 
compound this problem. As is well known, the mass limit of detection of 
inductive NMR detectors improves as they are scaled down~\cite{Olson1995}. 
On this basis, a number of different micro-NMR detector designs have been 
proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. 
In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, 
planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline 
detectors~\cite{stripline_jan}. 
Significant research has gone into developing micro-NMR detectors for flow probes, 
where the sample container takes the form of a fixed capillary into which the sample
must be injected. Only a few designs that allow insertion of a removable microfluidic 
device into the detector have been described \todo{REF Graeme, Spengler, Korvink et al}.

@@

\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
\caption{Exploded view of he probe design (left) and assembled probe (right). 
Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a 
generic mounting point for the NMR detector assembly(red). 
A microfluidic device (1) can be inserted from the top of the probe. 
The device is held in place by a spacer (4) between the detector planes (3 and 5) 
ensuring alignment of the sample chamber with the sensitive area on the PCB planes. 
The X channel frequency is controlled by a 
modular PCB insert (6). The modular NMR detector is made up of parts 3 to 6 and is 
connected to the base plate PCB (8) through standard coaxial (SMP) connectors. 
The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) 
and, auxiliary support disks (12).}
\label{fig:probe-explode} 
\end{figure}

The probe is composed of three main assemblies: A) probe base; B) scaffold assembly; 
C) detector assembly (figure~\ref{fig:probe}). 
The  base (blue in figure~\ref{fig:probe-explode}) and the scaffold assembly 
(green in figure~\ref{fig:probe-explode}) together make the skeleton of the probe. 
Both the base and scaffold assembly are made from standard aluminium profiles. 
The base contains the BNC connectors for RF (Radio Frequency) input. 
These BNC connectors are connected to semi-rigid coaxial cables for 
RF transport in the probe.

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with 
precision machined parts at either end(scaffold support disks (10)). 
The semi-rigid cables are  threaded through these hollow aluminium tubes 
to reach the detector assembly. 
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly. 
In our case, these were laser cut from 5~mm thick PMMA sheets, 
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 8) is held in place on the top of the probe skeleton by
the detector support rods (9), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permantly fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. It also provides 
capacitors (7) for secondary tuning and matching.
The detector assembly is connected to through a pair of
low-loss SMP connectors (14 in figure~\ref{fig:ProbePhoto}).
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for 
fine tuning and matching 
at the magnet through tuning rods (13) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular 
axial bore providing access from the bottom of the probe, which can be used for 
temperature and environmental control and/or fluidic connections to the sample as
needed.
The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an 
RF-insert (6). The detector used here is based on a planar transmission line geometry 
as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper 
planes, each with a constriction at the centre.  This geometry gives rise to an 
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field 
and the detection sensitivity
onto the sample area. 
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary 
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown here) is fixed to the auxiliary disk (2) 
and the scaffold assembly with screws. 
An exchangeable microfluidic device (1) can be inserted from the top of the detector. 
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ. 
The microfluidic device is held in place by the spacer 
between the two PCB planes coinciding the sample chamber with the constriction on the 
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment. 
Since the detector assembly is attached to the probe base through SMP 
connectors, it can easily be exchanged. 
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.
\par
\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. 
A has an O.D. of 44.45 mm, in B, circuit elements of X channel are integrated on the 
PCB itself making it compact (38 mm O.D.). Detachable SMP connectors (14) are used to 
connect the RF insert (6) and the detector assembly. }
\label{fig:ProbePhoto}
\end{figure}
Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. 
However, in (B) the circuitry of the RF insert (6) is integrated on the PCB plane (5), 
making the design more compact.
 Probe (A) is compatible with a Varian 600 ultra ) of
shield 14.1 T magnet, with anouter diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an 
outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a 
Bruker narrow bore shim stack. 
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with 
wide bore magnets with spacers or gradient stack to keep the probe centred.

@@

The double resnance circuit is based on the design shown in figure~\ref{fig:circuit}. 
%The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger 
%sample volumes for some cases. 
The transmission line detector is tuned to the desired proton 
Larmor frequency by chip capacitors located at its four corners, 
as well as a non-magnetic trimmer capacitor ($C_6$). Two primary 
matching capacitors ($C_5$ and $C_5'$) bring the impedance into the 
vicinity of 50$\Omega$. A short microstrip 
with a specific impedance of 50$\Omega$ 
on the PCB then provides a connection to the secondary tuning and matching elements on the TMPCB ($C_1$ and $C_2$).
The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert, in combination with
the complex admittance of the detector at the X channel frequency.
To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
used commercially available flat copper coils of 8 mm diameter and 3.5 turns \todo{check values} in the case of 
\textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz 
could be achieved without $L_1$.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe. 
Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).
\todo{modify figure to represent connections to detector structure properly, and include PCB microstrip
transmission line}
}
\label{fig:circuit}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
%\begin{itemize}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%\end{itemize}
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed in Solidworks (Solidworks, Dassault Syst\`{e}mes). 
Prefabricated profiles made from 6061-T3 aluminium (Aluminum Warehouse, UK) were used for the
 mechanical structure of the probe
(base platform, scaffold tubes, sleeve). 
A few customised precision-machined parts (scaffold support disks, top disk) were obtained from 
ProtoLabs (Telford, UK) after providing CAD files. A small number parts were machined in-house
 (detector support rods, auxiliary support disks). 
 All  electronic components including semi-rigid transmission lines were purchased from DigiKey Ltd. 
 Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK). Microfluidic 
devices were designed on AutoCAD. PMMA sheets were cut to desired size and functionality (holes or channels) using a 
laser engraving system  (HPC Laser L3040), 
and then bonded using the protocol described in~\cite{yilmaz_bonding}.

The precise dimensions of the detector were optimised for a given sample volume using 
finite element calculations in COMSOL, as described in \cite{gream_2016}. 
The RF response of the probe circuit was simulated using a symbolic  
network analysis code~\cite{gream-thesis} in order to estimate appropriate component values. Final tuning
was done by trial and error using an Agilent FieldFox 4 GHz network analyser. 
PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) 
for manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto} A) proved adequate for some purposes, but limited resolution to about 10 Hz.
A high-quality Teflon-based RF PCB material (RO3035, Rogers Corp., USA) was therefore used for optimal 
performance in both sensitivity and resolution (\fig{fig:ProbePhoto} B).
The probe skeleton was assembled from prefabricated aluminium tubes with the  precision-machined scaffold
disks using brass screws. Semi-rigid transmission lines were then threaded through the tubes, and the TMPCB plate was 
soldered on top. The detector planes (3 and 5) and the PMMA spacer between them were assembled using short bits
of 0.5~mm magnet wire, which were soldered to the appropriate pads in the four corners of the detector structure.

NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 ultra shield 14.1 T magnet.  
Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T 
magnet. 
Sodium acetate and $^{15}$N labeled urea were purchased from Merek \todo{Address?} and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par

@@

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
\caption{
Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 
60 MHz (\textsuperscript{15}N frequency at 14 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
Probe can be tuned to 2 frequencies at a time, above results were measured in 
pairs of 600 MHz with 60 MHz and 500 MHz with125 MHz. Decoupling can be performed at all the 
frequencies as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm} 
\end{figure}

@@

\fig{fig:1H-nutation} shows the $^1$H nutation diagram of the water peak in an aqueous solution of 
100~mM $^{15}$N-urea  measured at 600~MHz. The RF field shows good homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
ratio of more than 90\%. The probe generates 100~kHz nutation frequency from 100~W input power both at 
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$. 
The detector geometry has been optimised for a sample volume of 5~$\mu$l. It compares reasonably well to
the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.\todo{REF} for single-frequency detector 
of half this size at a Larmor frequency of 300~MHz.

@@

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.
\todo{fix typo in the x-axis label}
}
\label{fig:15N-nutation} 
\end{figure}

@@

Even though the resolution of the proton spectra still needs to be improved, it is sufficient to analyse
complex mixtures. The proton spectrum of DMEM (Dulbecco modified Eagle's medium) cell growth medium acquired with 256 
scans in 20 mins is shown in figure~\ref{fig:media-spec}. This demonstrates the suitability of this probe 
for metabolomic studies of microfluidic cultures of cells, tissues, and small organisms.

Figure~\ref{fig:HSQC} demonstrates proton-detected double resonance experiments in the current setup. 
The left panel shows a $^{13}$C-$^{1}$H heteronuclear single quantum correlation (HSQC) spectrum, acquired in 12 mins 
(32 t$_1$ increments and 16 scans) 
from a 2.5 $\mu$l sample of 100 mM u-$^{13}$C-glucose dissolved in water. The right panel shows a 
$^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) 
from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7. 
All expected cross peaks are present in the spectrum. The ability to obtain meaningful  \textsuperscript{1}H-
\textsuperscript{15}N correlation spectra from such small samples could prove very useful in the context of
proteins that are difficult to express and therefore only available in small quantities. The integration of
protein NMR and microfluidic technology also opens new possibilities for high-throughput kinetics and 
binding studies.

>>>>

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\address[1]{School of Chemistry, University of Southampton, Southampton SO17 1BJ, United Kingdom}
%\date{\today}
%\setcounter{Maxaffil}{0}
%\renewcommand\Affilfont{\itshape\footnotesize}
%\maketitle
%\clearpage

@@

Microfluidic NMR (Nuclear Magnetic Resonance) can probe chemical or bio-chemical reactions, including the metabolism of cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment. We present a dual-channel modular probe assembly for  high efficiency microfluidic-NMR. The samples are contained in exchangeable, flow compatible planar microfluidic devices. The detector including the tuning and matching circuitry of the probe is modular and allows the use of different detectors optimised for different experimental conditions on the same probe base. The complete probe can be built from easily available parts. The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit board) materials. The probe has a limit of detection of 1.18 nmol s$^{-1/2}$, resolution of 3.35 Hz and, excellent B$_{1}$ homogeneity. The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel (\textsuperscript{13}C or \textsuperscript{15}N) frequencies. We have successfully acquired \textsuperscript{1}H-\textsuperscript{13}C and \textsuperscript{1}H-\textsuperscript{15}N heteronuclear correlation spectrum (HSQC). Particularly, \textsuperscript{1}H-\textsuperscript{15}N HSQC spectrum of 1 mM \textsuperscript{15}N labeled ubiquitin from 2.5 $\mu$l of sample volume.

@@

%\clearpage

@@

molecular structure determination~\cite{wuthrich1990protein}, metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, reaction 

@@

NMR spectroscopy can provide a useful complementary readout capability 
for microfluidic devices. For example, the metabolic activity of cell cultures 
can be followed non-invasively by NMR throughout the course of the experiment, 
while effects on cell differentiation can still be analysed by a (destructive) 
transcriptomic analysis at the end. Unfortunately, the sensitivity 
of NMR is much lower than that of optical techniques. 
The small volumes involved in microfluidic systems
 (typically in the range of 1~$\mu$l) 
compound this problem. As is well known, the mass limit of detection of 
inductive NMR detectors improves as they are scaled down~\cite{Olson1995}. 
On this basis, a number of different micro-NMR detector designs have been 
proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. 
In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, 
planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline 
detectors~\cite{stripline_jan}. 
Significant research has gone into developing micro-NMR detectors for flow probes, 
where the sample container takes the form of a fixed capillary into which the sample
must be injected. Only a few designs that allow insertion of a removable microfluidic 
device into the detector have been described~\cite{Spengler-2014,Spengler-2016,gream_2016}.

@@

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
\caption{Exploded view of he probe design (left) and assembled probe (right). 
Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a 
generic mounting point for the NMR detector assembly(red). 
A microfluidic device (1) can be inserted from the top of the probe. 
The device is held in place by a spacer (4) between the detector planes (3 and 5) 
ensuring alignment of the sample chamber with the sensitive area on the PCB planes. 
The X channel frequency is controlled by a 
modular PCB insert (6). The modular NMR detector is made up of parts 3 to 6 and is 
connected to the base plate PCB (8) through standard coaxial (SMP) connectors. 
The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) 
and, auxiliary support disks (12).}
\label{fig:probe-explode} 
\end{figure}

The probe is composed of three main assemblies: A) probe base; B) scaffold assembly; 
C) detector assembly (\fig{fig:probe}). 
The  base (blue in \fig{fig:probe-explode}) and the scaffold assembly 
(green in \fig{fig:probe-explode}) together make the skeleton of the probe. 
Both the base and scaffold assembly are made from standard aluminium profiles. 
The base contains the BNC connectors for RF (Radio Frequency) input. 
These BNC connectors are connected to semi-rigid coaxial cables for 
RF transport in the probe.

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with 
precision machined parts at either end(scaffold support disks (10)). 
The semi-rigid cables are  threaded through these hollow aluminium tubes 
to reach the detector assembly. 
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly. 
In our case, these were laser cut from 5~mm thick PMMA sheets, 
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 8) is held in place on the top of the probe skeleton by
the detector support rods (9), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permantly fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. It also provides 
capacitors (7) for secondary tuning and matching.
The detector assembly is connected to through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for 
fine tuning and matching 
at the magnet through tuning rods (13) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular 
axial bore providing access from the bottom of the probe, which can be used for 
temperature and environmental control and/or fluidic connections to the sample as
needed.
The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an 
RF-insert (6). The detector used here is based on a planar transmission line geometry 
as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper 
planes, each with a constriction at the centre.  This geometry gives rise to an 
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field 
and the detection sensitivity
onto the sample area. 
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary 
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown here) is fixed to the auxiliary disk (2) 
and the scaffold assembly with screws. 
An exchangeable microfluidic device (1) can be inserted from the top of the detector. 
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ. 
The microfluidic device is held in place by the spacer 
between the two PCB planes coinciding the sample chamber with the constriction on the 
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment. 
Since the detector assembly is attached to the probe base through SMP 
connectors, it can easily be exchanged. 
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.
\par
\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. 
A has an O.D. of 44.45 mm, in B, circuit elements of X channel are integrated on the 
PCB itself making it compact (38 mm O.D.). Detachable SMP connectors (14) are used to 
connect the RF insert (6) and the detector assembly. }
\label{fig:ProbePhoto}
\end{figure}
\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. 
However, in (B) the circuitry of the RF insert (6) is integrated on the PCB plane (5), 
making the design more compact.
 Probe (A) is compatible with a Varian 600 ultra ) of
shield 14.1 T magnet, with anouter diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an 
outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a 
Bruker narrow bore shim stack. 
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with 
wide bore magnets with spacers or gradient stack to keep the probe centred.

@@

The double resnance circuit is based on the design shown in \fig{fig:circuit}. 
%The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger 
%sample volumes for some cases. 
The transmission line detector is tuned to the desired proton 
Larmor frequency by chip capacitors located at its four corners, 
as well as a non-magnetic trimmer capacitor ($C_6$). Two primary 
matching capacitors ($C_5$ and $C_5'$) bring the impedance into the 
vicinity of 50$\Omega$. A short microstrip 
with a specific impedance of 50$\Omega$ 
on the PCB then provides a connection to the secondary tuning and matching elements on the TMPCB ($C_1$ and $C_2$).
The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert, in combination with
the complex admittance of the detector at the X channel frequency.
To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
used commercially available flat copper coils of 5 mm diameter and 4.5 turns in the case of 
\textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz 
could be achieved without $L_1$.

\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe. 
Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).
}
\label{fig:circuit}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
%\begin{itemize}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%\end{itemize}
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed in Solidworks (Solidworks, Dassault Syst\`{e}mes). 
Prefabricated profiles made from 6061-T3 aluminium (Aluminum Warehouse, UK) were used for the
 mechanical structure of the probe
(base platform, scaffold tubes, sleeve). 
A few customised precision-machined parts (scaffold support disks, top disk) were obtained from 
ProtoLabs (Telford, UK) after providing CAD files. A small number parts were machined in-house
 (detector support rods, auxiliary support disks). 
 All  electronic components including semi-rigid transmission lines were purchased from DigiKey Ltd. 
 Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK). Microfluidic 
devices were designed on AutoCAD. PMMA sheets were cut to desired size and functionality (holes or channels) using a 
laser engraving system  (HPC Laser L3040), 
and then bonded using the protocol described in~\cite{yilmaz_bonding}.

The precise dimensions of the detector were optimised for a given sample volume using 
finite element calculations in COMSOL, as described in \cite{gream_2016}. 
The RF response of the probe circuit was simulated using a symbolic  
network analysis code~\cite{gream-thesis} in order to estimate appropriate component values. Final tuning
was done by trial and error using an Agilent FieldFox 4 GHz network analyser. 
PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) 
for manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited resolution to about 10 Hz.
A high-quality Teflon-based RF PCB material (RO3035, Rogers Corp., USA) was therefore used for optimal 
performance in both sensitivity and resolution (\fig{fig:ProbePhoto}(B)).
The probe skeleton was assembled from prefabricated aluminium tubes with the  precision-machined scaffold
disks using brass screws. Semi-rigid transmission lines were then threaded through the tubes, and the TMPCB plate was 
soldered on top. The detector planes (3 and 5) and the PMMA spacer between them were assembled using short bits
of 0.5~mm magnet wire, which were soldered to the appropriate pads in the four corners of the detector structure.

NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 ultra shield 14.1 T magnet.  
Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T 
magnet. 
Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich,UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par

@@

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
\caption{
Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 
60 MHz (\textsuperscript{15}N frequency at 14 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
Probe can be tuned to 2 frequencies at a time, above results were measured in 
pairs of 600 MHz with 60 MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the 
frequencies as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm} 
\end{figure}

@@

\fig{fig:1H-nutation} shows the $^1$H nutation diagram of the water peak in an aqueous solution of 
100~mM $^{15}$N-urea  measured at 600~MHz. The RF field shows good homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
ratio of more than 90\%. The probe generates 100~kHz nutation frequency from 100~W input power both at 
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$. 
The detector geometry has been optimised for a sample volume of 5~$\mu$l. It compares reasonably well to
the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for single-frequency detector 
of half this size at a Larmor frequency of 300~MHz.

@@

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.}
\label{fig:15N-nutation} 
\end{figure}

@@

Even though the resolution of the proton spectra still needs to be improved, it is sufficient to analyse
complex mixtures. The proton spectrum of DMEM (Dulbecco modified Eagle's medium) cell growth medium acquired with 256 
scans in 20 mins is shown in \fig{fig:media-spec}. This demonstrates the suitability of this probe 
for metabolomic studies of microfluidic cultures of cells, tissues, and small organisms.

\fig{fig:HSQC} demonstrates proton-detected double resonance experiments in the current setup. 
The left panel shows a $^{13}$C-$^{1}$H heteronuclear single quantum correlation (HSQC) spectrum, acquired in 12 mins 
(32 t$_1$ increments and 16 scans) 
from a 2.5 $\mu$l sample of 100 mM u-$^{13}$C-glucose dissolved in water. The right panel shows a 
$^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) 
from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7. 
All expected cross peaks are present in the spectrum. The ability to obtain meaningful  \textsuperscript{1}H-
\textsuperscript{15}N correlation spectra from such small samples could prove very useful in the context of
proteins that are difficult to express and therefore only available in small quantities. The integration of
protein NMR and microfluidic technology also opens new possibilities for high-throughput kinetics and 
binding studies.
